\documentclass{resume}

\usepackage{fontawesome}
\setmainfont{Arial}

\name{Rik L.E.M. Ubaghs}

\address{\faLink{ rlemubaghs.com } \faGithub{ https://github.com/rlemubaghs } \faMapMarker{ Zurich, Switzerland }}
\address{\faEnvelope{ ubaghs@aragolabs.com } \faPhone{ +31 6 51 45 01 60 }} 

\begin{document}

\begin{sections}{Bio}

{I am a neural engineer specialized in neurotechnology. My areas of expertise are biomedical imaging, medical technology, brain-machine interfaces, and data analysis.
\\In my work, I am mostly interest in bridging the gab between experimental (neuro)technology and practical applications in the medical domain.}

\end{sections}

\begin{sections}{Education}

{\bf ETH Zurich, Zurich, Switzerland} \hfill {July 2017 - May 2023} 
\\ {\textit {Ph.D. Neurotechnology}} \hfill

{\bf University of Amsterdam, Amsterdam, the Netherlands} \hfill {Sept 2014 - June 2016}
\\{\textit {Research Master Brain and Cognitive Sciences, Cum Laude}} 

{\bf Maastricht University, Maastricht, the Netherlands} \hfill {Sept 2011 - June 2014} 
\\{\textit {Bachelor Psychology and Neuroscience, Cum Laude}} 

\end{sections}

\begin{sections}{Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l}
Languages: \ & Dutch (Native), English (Fluent), German (Basic) \\
Programming: \ & Python, Matlab, Rust, R, SQL \\
Skills: \ & Data Science, Biomedical Imaging, Microscopy, Mechanical design 
\end{tabular}

\end{sections}

\begin{sections}{Research Positions}

{\bf AragoLabs (@Inst. of Neuroinformatics, ETH Zurich, Zurich, Switzerland)} \hfill {June 2023 - Current} 
\\{\textit{Co-founder}}
\\- Development of a miniaturized microscope for tumor visualization and classification during neurosurgery.

{\bf Inst. of Neuroinformatics, ETH Zurich, Zurich, Switzerland} \hfill {July 2017 – June 2023} 
\\{\textit{Ph.D. Candidate}}
\\- Development of a MRI compatible florescence microscope (full-cycle product design).
\\- Design of a paradigm to combine microscopy and MR imaging methods in awake rodents. 
\\- Design of data pipelines for multi-modal data analysis.

{\bf Center for Neuroengineering, Duke University, Durham, USA} \hfill {Dec 2015 – Nov 2016} 
\\{\textit{Visiting Scientist}}
\\- Development of hybrid brain decoding methods in Non-human Primates.

{\bf Swammerdam Institute for Life Sciences, Amsterdam, The Netherlands} \hfill {Aug 2015 – Dec 2015} 
\\{\textit{Internship}}
\\- Experimental design for sensory integration in rodents.
\\- Design of data analysis methods for high dimensional data.

{\bf Spinoza Center for Neuroimaging, Amsterdam, The Netherlands} \hfill {Nov 2014 - Dec 2015} 
\\{\textit{Junior Research Scientist}}
\\- MR operator.
\\- Design and supervision of several large research projects.

\end{sections}

\cleardoublepage

\begin{sections}{Industry Positions}

{\bf Agora Technology, Maastricht, The Netherlands} \hfill {Nov 2016 - Feb 2018} 
\\{\textit{Founder}}
\\- Built data solutions that aimed at streamlining/automating the workflow of medical facilities, especially focusing on surgical equipment.
\\- We focused on internal logistics, and the creation, maintenance, and analysis of large-scale medical equipment databases using ML/DL.
\\- Clients included Maastricht University Medical Center and Medtronic. 

\end{sections}

\begin{sections}{Extracurricular Positions}

{\bf Natural Movements, The Netherlands} \hfill {March 2007 - May 2012} 
\\{\textit{Co-Founder}}
\\- Natural Movements is a non-profit organization that aims to engage underprivileged youth in the local community through behavioral coaching and physical education.
\\- We worked together with social service organisations to provide youth with any additional support they required.

\end{sections}

\begin{sections}{Publications}

{\bf Research Papers:}
\\
{- Simultaneous single-cell calcium imaging of neuronal population activity and brain-wide BOLD fMRI
Ubaghs, R.L.E.M., Boehringer, R., Marks, M., Hesse, H.K., Yanik, M.F., Zerbi, V., Grewe, B.F., bioRxiv 2023.11.14.566368; doi: https://doi.org/10.1101/2023.11.14.566368}
\\
\\
{\bf Conference Abstracts:}
\\{- Ubaghs, R.L.E.M., Böhringer, R., Marks, M., Yanik, M.F. and Grewe, B.F., The Effect of Somatostatin+ Interneurons on the Negative BOLD Response. Proc. Intl. Soc. Mag. Reson. Med. 29 (2021)}
\\{- Ubaghs, R.L.E.M., Dermutz, H., Böhringer, R., Marks, M., Yanik, M.F. and Grewe, B.F., Shaping the BOLD signal through Excitatory and Inhibitory Interaction. Proc. Intl. Soc. Mag. Reson. Med. 28 (2020)}

\end{sections}

\begin{sections}{Honors}

{\bf Committees:}
\\
{Educational Committee, IIS, University of Amsterdam} \hfill {Sept 2014 - June 2015} 
\\
{Vice-President Student Council, FPN, Maastricht University} \hfill {Sept 2012 - June 2013} 
\\
{Program Committee, FPN, Maastricht University} \hfill {Sept 2012 - June 2013}
\\
\\
{\bf Grants:}
\\
{Hendrik Muller Memorial Foundation} \hfill {2016}
\\
{Bekker - La Bastide Memorial Foundation} \hfill {2015}
\\
{Vrijvrouwe van Renswoude Foundation} \hfill {2015}

\end{sections}

\end{document}